Does It Scale? Static Output Approximation of PHP Web Applications Using Symbolic Execution

### 2017-01-14 paper.tex
4.4.1 refactored

\subsubsection{What literals did we miss?}\label{WhatLiteralsDidWeMiss?}
Our initial approach to understand missed output candidates is to find out
whether their surrounding program code was not accessed/accessible, and if so,
why. Of special interest are those output candidates that are located in HTML
files (possibly with nested PHP), or located in a function definition. Plain
HTML files do not require any further execution (of course, unless PHP scripts
are embedded) and represent output candidates that just need to be included
properly to be part of the output. Aside, output candidates that are part of a
function definition are only missed if the corresponding function is never
called at runtime.

We started classifying missed output candidates by their string literal
context. As the classification statistics in Figure \ref{coverage} illustrate,
for almost all systems (except for \textsf{AddressBook} and \textsf{TimeClock})
not-reached output candidates had a function context. Note that
\textsf{SchoolMate} was excluded from the diagram since our analysis reached
all output candidates for that system.

@@

>>>>

\subsubsection{What literals did we miss?}\label{WhatLiteralsDidWeMiss?}
Our initial approach to understand missed output candidates is to find out
whether their surrounding program code was not accessed/accessible, and if so,
why. We are interested in those output candidates that are located in HTML
files (possibly with nested PHP), or located in a function definition. Plain
HTML files do not require any further execution and represent output candidates
that just need to be included properly to be part of the output. Aside, output
candidates that are part of a function definition are only missed if the
corresponding function is never called at runtime.

We started classifying missed output candidates by their string literal
context. As the classification statistics in Figure \ref{coverage} illustrate,
for almost all systems (except for \textsf{AddressBook} and \textsf{TimeClock})
not-reached output candidates had a function context.

%Note that \textsf{SchoolMate} was excluded from the diagram since our analysis
% reached all output candidates for that system.

@@

\section{Conclusion}
